PM Component Paper Correlation Plots

### 2021-05-31 code/data-analysis/factor-analysis.Rmd
update plot lables and shapes

Sources <- c("Soil", "Metal", "Traffic", "Biomass", "Coal", "Salt", "Oil", "Steel")

@@

```{r - Single Tracer Mass Apportionment - Combination 1}
dt.mass.app.c1 <- dt.pmc.daily %>% 
  mutate(Soil = so.coef(high.load, 'SI') * SI,
         Metal = so.coef(high.load, 'PB') * PB,
         Traffic = so.coef(high.load, 'OC') * OC,
         Biomass = so.coef(high.load, 'K') * K,
         Coal = so.coef(high.load, 'SO4') * SO4,
         Salt = so.coef(high.load, 'CL') * CL,
         Oil = so.coef(high.load, 'NI') * NI,
         Steel = so.coef(high.load, 'FE') * FE) %>% 
  select(Site.ID, Date, PM, Sources) %>% 
  inner_join(dt.sites) %>% 
  pivot_longer(cols = c('PM', Sources),
               names_to = "Source",
               values_to = "Mass")

@@

```{r - Single Tracer Mass Apportionment - Combination 2}
dt.mass.app.c2 <- dt.pmc.daily %>% 
  mutate(Soil = so.coef(high.health, 'SI') * SI,
         Metal = so.coef(high.health, 'PB') * PB,
         Traffic = so.coef(high.health, 'NO3') * NO3,
         Biomass = so.coef(high.health, 'K') * K,
         Coal = so.coef(high.health, 'SO4') * SO4,
         Salt = so.coef(high.health, 'CL') * CL,
         Oil = so.coef(high.health, 'NI') * NI,
         Steel = so.coef(high.health, 'MN') * MN) %>% 
  select(Site.ID, Date, PM, Sources) %>% 
  inner_join(dt.sites) %>% 
  pivot_longer(cols = c('PM', Sources),
               names_to = "Source",
               values_to = "Mass")

>>>>

Sources <- c("Soil", "Metals", "Traffic", "Biomass", "Coal", "Salt", "Oil", "Steel")

@@

```{r - Single Tracer Mass Apportionment - Combination 1}
dt.mass.app.c1 <- dt.pmc.daily %>% 
  mutate(Soil = so.coef(high.load, 'SI') * SI,
         Metals = so.coef(high.load, 'PB') * PB,
         Traffic = so.coef(high.load, 'OC') * OC,
         Biomass = so.coef(high.load, 'K') * K,
         Coal = so.coef(high.load, 'SO4') * SO4,
         Salt = so.coef(high.load, 'CL') * CL,
         Oil = so.coef(high.load, 'NI') * NI,
         Steel = so.coef(high.load, 'FE') * FE) %>% 
  select(Site.ID, Date, PM, Sources) %>% 
  inner_join(dt.sites) %>% 
  pivot_longer(cols = c('PM', Sources),
               names_to = "Source",
               values_to = "Mass")

@@

```{r - Single Tracer Mass Apportionment - Combination 2}
dt.mass.app.c2 <- dt.pmc.daily %>% 
  mutate(Soil = so.coef(high.health, 'SI') * SI,
         Metals = so.coef(high.health, 'PB') * PB,
         Traffic = so.coef(high.health, 'NO3') * NO3,
         Biomass = so.coef(high.health, 'K') * K,
         Coal = so.coef(high.health, 'SO4') * SO4,
         Salt = so.coef(high.health, 'CL') * CL,
         Oil = so.coef(high.health, 'NI') * NI,
         Steel = so.coef(high.health, 'MN') * MN) %>% 
  select(Site.ID, Date, PM, Sources) %>% 
  inner_join(dt.sites) %>% 
  pivot_longer(cols = c('PM', Sources),
               names_to = "Source",
               values_to = "Mass")

### 2021-05-31 code/data-viz/correlation.Rmd
plot, table, map
update plot lables and shapes

---
title: "R Notebook"
---

@@

@@

jpeg(here('output','plot','corr-us.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
corrplot(corr, type = "lower",  method = 'number',
         tl.col = "black", tl.srt = 45, number.cex=0.65,
         col = rev(brewer.pal(n = 10, name = "RdGy"))) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 14, hjust = 1, face='bold'),
        axis.text.y = element_text(angle = 0, vjust = 1, 
                                   size = 14, hjust = 1, face='bold'),
        legend.title = element_blank())
dev.off()
```

```{r - Region}
dt.pmc<-dt.pmc[order(dt.pmc$Region.IV),]

jpeg(here('output','plot','corr-region.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
par(mfrow=c(2,2))
for(i in unique(dt.pmc$Region)) {
  data<- subset(dt.pmc, Region==i)
  corr <- data %>%
    select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
    na.omit %>%
    cor()
  corrplot(corr, type = "lower",
           tl.col = "black", tl.srt = 45, number.cex=0.65,
           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                     size = 14, hjust = 1, face='bold'),
          axis.text.y = element_text(angle = 0, vjust = 1, 
                                     size = 14, hjust = 1, face='bold'),
          legend.title = element_blank())
}
dev.off()
```

```{r - Urbanicity}
jpeg(here('output','plot','corr-urbanicity.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
par(mfrow=c(2,2))
for(i in unique(dt.pmc$Loc.Set)) {
  data<- subset(dt.pmc, Loc.Set==i)
  corr <- data %>%
    select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
    na.omit %>%
    cor()
  corrplot(corr, type = "lower",
           tl.col = "black", tl.srt = 45, number.cex=0.65,
           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                     size = 14, hjust = 1, face='bold'),
          axis.text.y = element_text(angle = 0, vjust = 1, 
                                     size = 14, hjust = 1, face='bold'),
          legend.title = element_blank())
}
dev.off()
```

>>>>

---
title: "PM Component Paper Correlation Plots"
author: "Fatemeh Kazemi"
date: "01-31-2021"
---

@@

```{r}
cmp.main.labels <- c("As", "Ca", "Cl", "Cu", "Fe", "K",  "Mg", "Mn", "Na", "Ni",
                     "$NO[3]^'-'", "OC", "Pb", "Se", "Si",
                     "$SO[4]^'2-'", "V", "Zn", "$PM[2.5]")
```

@@

colnames(corr) <- cmp.main.labels
rownames(corr) <- cmp.main.labels

jpeg(here('output','plot','corr-us.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
corrplot(corr, type = "lower",  method = 'number',
         tl.col = "black", tl.srt = 45, number.cex=0.65, title = "US",mar=c(0,0,1,0),
         col = rev(brewer.pal(n = 10, name = "RdGy")))
dev.off()
```

```{r - Region}
dt.pmc<-dt.pmc[order(dt.pmc$Region.IV),] %>% 
  mutate(Region = ifelse(Region == "W", "West",
                         ifelse(Region == "MW", "Midwest",
                                ifelse(Region == "S", "South", "Northeast"))))

jpeg(here('output','plot','corr-region.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
par(mfrow=c(2,2))
for(i in unique(dt.pmc$Region)) {
  data<- subset(dt.pmc, Region==i)
  corr <- data %>%
    select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
    na.omit %>%
    cor()
  colnames(corr) <- cmp.main.labels
  rownames(corr) <- cmp.main.labels
  corrplot(corr, type = "lower",
           tl.col = "black", tl.srt = 45, number.cex=0.65, tl.cex = 0.75,
           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0))
}
dev.off()
```

```{r - Urbanicity}
jpeg(here('output','plot','corr-urbanicity.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
par(mfrow=c(2,2))
dt.pmc <- dt.pmc %>% arrange(Loc.Set)
for(i in unique(dt.pmc$Loc.Set)) {
  data<- subset(dt.pmc, Loc.Set==i)
  corr <- data %>%
    select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
    na.omit %>%
    cor()
  colnames(corr) <- cmp.main.labels
  rownames(corr) <- cmp.main.labels
  corrplot(corr, type = "lower",
           tl.col = "black", tl.srt = 45, number.cex=0.65, tl.cex = 0.75,
           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) 
}
dev.off()
```
